Summary of Performance Measures for Scenario OR

### 2024-08-29 doc/performance.Rmd
new version of results tables for bross and hybrid with the edited codes

load("results/scenario/bross.RData")
load("results/scenario/hybrid.RData")
load("results/scenario/lasso.RData")
load("results/scenario/enet.RData")
load("results/scenario/ga.RData")
load("results/scenario/xgboost.RData")
load("results/scenario/rf.RData")
load("results/scenario/forward.RData")
load("results/scenario/backward.RData")

@@

est_bross    <- RD_bross[ind,]
est_hybird   <- RD_hybrid[ind,]
est_lasso    <- RD_lasso[ind,]
est_enet     <- RD_enet[ind,]
est_ga       <- RD_ga[ind,]
est_xgboost  <- RD_xgboost[ind,]
est_rf       <- RD_rf[ind,]
est_forward  <- RD_forward[ind,]
est_backward <- RD_backward[ind,]

est_bross$model    <- "bross"
est_hybird$model   <- "hybrid"
est_lasso$model    <- "lasso"
est_enet$model     <- "enet"
est_ga$model       <- "ga"
est_xgboost$model  <- "xgboost"
est_rf$model       <- "rf"
est_forward$model  <- "forward"
est_backward$model <- "backward"
```

@@

```{r bind}
est <- rbind(est_bross, est_hybird, est_lasso, est_enet, 
             est_ga, est_xgboost, est_rf,
             est_forward, est_backward)

est$model <- as.factor(est$model)
levels<- c("bross", "hybrid", "lasso", "enet", "ga", "xgboost", "rf", "forward", "backward")
est$model <- factor(est$model, levels = levels)
levels(est$model)
```

>>>>

load("results/scenario/bross.RData")
load("results/scenario/hybrid.RData")
load("results/scenario/lasso.RData")
load("results/scenario/enet.RData")
load("results/scenario/ga.RData")
load("results/scenario/xgboost.RData")
load("results/scenario/rf.RData")
load("results/scenario/forward.RData")
load("results/scenario/backward.RData")
load("results/scenario/kitchen.RData")

@@

est_bross    <- RD_bross[ind,]
est_hybird   <- RD_hybrid[ind,]
est_lasso    <- RD_lasso[ind,]
est_enet     <- RD_enet[ind,]
est_ga       <- RD_ga[ind,]
est_xgboost  <- RD_xgboost[ind,]
est_rf       <- RD_rf[ind,]
est_forward  <- RD_forward[ind,]
est_backward <- RD_backward[ind,]
est_kitchen  <- RD_kitchen[ind,]

est_bross$model    <- "bross"
est_hybird$model   <- "hybrid"
est_lasso$model    <- "lasso"
est_enet$model     <- "enet"
est_ga$model       <- "ga"
est_xgboost$model  <- "xgboost"
est_rf$model       <- "rf"
est_forward$model  <- "forward"
est_backward$model <- "backward"
est_kitchen$model  <- "kitchen"
```

@@

```{r bind}
est <- rbind(est_bross, est_hybird, est_lasso, est_enet, 
             est_ga, est_xgboost, est_rf,
             est_forward, est_backward, est_kitchen)

est$model <- as.factor(est$model)
levels<- c("bross", "hybrid", "lasso", "enet", "ga", "xgboost", "rf", "forward", "backward", "kitchen")
est$model <- factor(est$model, levels = levels)
levels(est$model)
```

### 2024-08-29 doc/performanceER.Rmd
new version of results tables for bross and hybrid with the edited codes

load("results/scenarioER/bross.RData")
load("results/scenarioER/hybrid.RData")
load("results/scenarioER/lasso.RData")
load("results/scenarioER/enet.RData")
load("results/scenarioER/ga.RData")
load("results/scenarioER/xgboost.RData")
load("results/scenarioER/rf.RData")
load("results/scenarioER/forward.RData")
load("results/scenarioER/backward.RData")

@@

est_bross    <- RD_bross.ER[ind,]
est_hybird   <- RD_hybrid_ER[ind,]
est_lasso    <- RD_lasso_ER[ind,]
est_enet     <- RD_enet_ER[ind,]
est_ga       <- RD_ga_ER[ind,]
est_xgboost  <- RD_xgboost_ER[ind,]
est_rf       <- RD_rf_ER[ind,]
est_forward  <- RD_forward[ind,]
est_backward <- RD_backward[ind,]

est_bross$model    <- "bross"
est_hybird$model   <- "hybrid"
est_lasso$model    <- "lasso"
est_enet$model     <- "enet"
est_ga$model       <- "ga"
est_xgboost$model  <- "xgboost"
est_rf$model       <- "rf"
est_forward$model  <- "forward"
est_backward$model <- "backward"
```

>>>>

load("results/scenarioER/bross.RData")
load("results/scenarioER/hybrid.RData")
load("results/scenarioER/lasso.RData")
load("results/scenarioER/enet.RData")
load("results/scenarioER/ga.RData")
load("results/scenarioER/xgboost.RData")
load("results/scenarioER/rf.RData")
load("results/scenarioER/forward.RData")
load("results/scenarioER/backward.RData")
load("results/scenarioER/kitchen.RData")

@@

est_bross    <- RD_bross.ER[ind,]
est_hybird   <- RD_hybrid_ER[ind,]
est_lasso    <- RD_lasso_ER[ind,]
est_enet     <- RD_enet_ER[ind,]
est_ga       <- RD_ga_ER[ind,]
est_xgboost  <- RD_xgboost_ER[ind,]
est_rf       <- RD_rf_ER[ind,]
est_forward  <- RD_forward[ind,]
est_backward <- RD_backward[ind,]
est_kitchen  <- RD_kitchen[ind,]

est_bross$model    <- "bross"
est_hybird$model   <- "hybrid"
est_lasso$model    <- "lasso"
est_enet$model     <- "enet"
est_ga$model       <- "ga"
est_xgboost$model  <- "xgboost"
est_rf$model       <- "rf"
est_forward$model  <- "forward"
est_backward$model <- "backward"
est_kitchen$model  <- "kitchen"
```

### 2024-08-29 doc/performanceOR.Rmd
new version of results tables for bross and hybrid with the edited codes

load("results/scenarioOR/bross.RData")
load("results/scenarioOR/hybrid.RData")
load("results/scenarioOR/lasso.RData")
load("results/scenarioOR/enet.RData")
load("results/scenarioOR/ga.RData")
load("results/scenarioOR/xgboost.RData")
load("results/scenarioOR/rf.RData")
load("results/scenarioOR/forward.RData")
load("results/scenarioOR/backward.RData")

@@

est_bross    <- RD_bross.OR[ind,]
est_hybird   <- RD_hybrid_OR[ind,]
est_lasso    <- RD_lasso_OR[ind,]
est_enet     <- RD_enet_OR[ind,]
est_ga       <- RD_ga_OR[ind,]
est_xgboost  <- RD_xgboost_OR[ind,]
est_rf       <- RD_rf_OR[ind,]
est_forward  <- RD_forward[ind,]
est_backward <- RD_backward[ind,]

est_bross$model    <- "bross"
est_hybird$model   <- "hybrid"
est_lasso$model    <- "lasso"
est_enet$model     <- "enet"
est_ga$model       <- "ga"
est_xgboost$model  <- "xgboost"
est_rf$model       <- "rf"
est_forward$model  <- "forward"
est_backward$model <- "backward"
```

@@

```{r bind}
est <- rbind(est_bross, est_hybird, est_lasso, est_enet, 
             est_ga, est_xgboost, est_rf,
             est_forward, est_backward)
est$model <- as.factor(est$model)
levels<- c("bross", "hybrid", "lasso", "enet", "ga", "xgboost", "rf", "forward", "backward")
est$model <- factor(est$model, levels = levels)
levels(est$model)
```

>>>>

load("results/scenarioOR/bross.RData")
load("results/scenarioOR/hybrid.RData")
load("results/scenarioOR/lasso.RData")
load("results/scenarioOR/enet.RData")
load("results/scenarioOR/ga.RData")
load("results/scenarioOR/xgboost.RData")
load("results/scenarioOR/rf.RData")
load("results/scenarioOR/forward.RData")
load("results/scenarioOR/backward.RData")
load("results/scenarioOR/kitchen.RData")

@@

est_bross    <- RD_bross.OR[ind,]
est_hybird   <- RD_hybrid_OR[ind,]
est_lasso    <- RD_lasso_OR[ind,]
est_enet     <- RD_enet_OR[ind,]
est_ga       <- RD_ga_OR[ind,]
est_xgboost  <- RD_xgboost_OR[ind,]
est_rf       <- RD_rf_OR[ind,]
est_forward  <- RD_forward[ind,]
est_backward <- RD_backward[ind,]
est_kitchen  <- RD_kitchen[ind,]

est_bross$model    <- "bross"
est_hybird$model   <- "hybrid"
est_lasso$model    <- "lasso"
est_enet$model     <- "enet"
est_ga$model       <- "ga"
est_xgboost$model  <- "xgboost"
est_rf$model       <- "rf"
est_forward$model  <- "forward"
est_backward$model <- "backward"
est_kitchen$model  <- "kitchen"
```

@@

```{r bind}
est <- rbind(est_bross, est_hybird, est_lasso, est_enet, 
             est_ga, est_xgboost, est_rf,
             est_forward, est_backward, est_kitchen)
est$model <- as.factor(est$model)
levels<- c("bross", "hybrid", "lasso", "enet", "ga", "xgboost", "rf", "forward", "backward", "kitchen")
est$model <- factor(est$model, levels = levels)
levels(est$model)
```
